---
title: "R Notebook"
output: html_notebook
---

# Loading in and Combining Red/White Datasets
```{r}
df = read.csv("Wine_Data/winequality-white.csv", sep=";")
```


```{r}
set.seed(100)
train_rows = sample(row.names(df), dim(df)[1]*0.8)
test_rows = setdiff(row.names(df), train_rows)

train_data = df[train_rows,] 
test_data = df[test_rows,]
```


```{r}
library(ggplot2)

ggplot(df,aes(x=quality)) +
  geom_histogram(binwidth = 1)
```

```{r}
library(reshape)

cor_matrix <- cor(df[-c(12)])

cor_mat_melt<-melt(round(cor_matrix,2))
## Heatmap for correlation among all variables
ggplot(cor_mat_melt,aes(x=X1,y=X2)) +
  geom_tile(aes(fill=value)) +
  scale_fill_gradientn(colours = c("blue", "white", "red"), limits = c(-1,1.0)) +
  geom_text(aes(label=value)) +
  guides(x = guide_axis(angle = 90))

```
# Linear Regression Model
## Model Construction
```{r}
lin_mod = lm(quality ~ ., data=train_data)

summary(lin_mod)
```

## Linear Regression Performance Train Set Performance
```{r}
library(forecast)

accuracy(lin_mod$fitted.values, train_data$quality)
```

## Linear Regression Test Set Performance
```{r}
test_pred = predict(lin_mod, newdata=test_data)
accuracy(test_pred, test_data$quality)
```

# kNN Regression Model
# Model Construction
```{r}
library(caret)
knn_model = knnreg(train_data[-c(12)], train_data$quality)

```

## kNN Regression Performance Train Set Performance
```{r}
library(forecast)

train_pred = predict(knn_model, train_data[-c(12)])

accuracy(train_pred, train_data$quality)
```

## kNN Regression Test Set Performance
```{r}
test_pred = predict(knn_model, test_data[-c(12)])
accuracy(test_pred, test_data$quality)
```

# Decision Tree Model
## Model Construction
```{r}
library(rpart)
DT_model = rpart(quality ~ ., method = "anova", data = train_data)
```

## Decision Tree Regression Performance Train Set Performance
```{r}
train_pred = predict(DT_model, train_data)
accuracy(train_pred, train_data$quality)
```

## Decision Tree Regression Performance Test Set Performance
```{r}
test_pred = predict(DT_model, test_data, method = "anova")
accuracy(test_pred, test_data$quality)
```

```{r}
library(rpart.plot)
rpart.plot(DT_model)
```

# SVM Regression Model
## Model Construction
```{r}
library(e1071)

svm_model = svm(quality~.,train_data)
```

## SVM Regression Performance Train Set Performance
```{r}
train_pred = predict(svm_model, train_data)
accuracy(train_pred, train_data$quality)
```

## SVM Regression Performance Test Set Performance
```{r}
test_pred = predict(svm_model, test_data, method = "anova")
accuracy(test_pred, test_data$quality)
```

